Rate of Information 

### 2019-01-23 cogsci/position-info.Rmd
working on yu et al section of intro

In Yu et al. (2016), the authors challenge the UID perspective through computing the unigram positional entropy within the text portion of the British National Corpus (BNC). We follow Yu et al. (2016) in using the following formula for each word position X of sentences of fixed length k from the corpus, where each $w$ is a word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position X divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$.

$$H(X) = \sum\limits_w p(w)\log\big(p(w)\big)$$

The result of this method can be plotted for each utterance length as an *entropy curve*, which can be visually compared across utterance length to observe the how the unigram entropy changes across absolute positions in each of the utterances

>>>>

Yu et al. (2016) challenges the UID hypothesis through examining the distribution of uncertainty across sentence positions within the text portion of the English-language British National Corpus (BNC). They partition the corpus by sentence length in number of words, and proceed for each sentence length $k$ within the corpus. for each word position X of sentences of fixed length k from the corpus, where each $w$ is a word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position X divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$.

$$H(X) = \sum\limits_w p(w)\log\big(p(w)\big)$$
With this measure, Yu et al. compute the unigram entropy at each position of sentences of each length within the corpus. The result of this method can be plotted for each utterance length as an *entropy curve*, which can be visually compared across utterance length to observe the how the unigram entropy changes across absolute positions in each of the utterances
